An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-01-13 paper.tex

\subsection*{Processed Data}
%
We developed a toolkit for data processing, GaitAnalysisToolKit v0.1.2,
\cite{Moore2014a}, for common gait computations and provide an example
processed trial to present the nature of the data. The tool was developed in
Python, is dependent on the SciPy Stack (NumPy, SciPy, matplotlib, Pandas, etc)
and Octave, and provides two main classes: one to do basic gait data cleaning
from D-Flow's output files, \verb|DFlowData|, and a second to compute common
gait variables of interest, \verb|GaitData|.

>>>>

\subsection*{Processed Data}
%
We developed a toolkit for data processing, GaitAnalysisToolKit v0.1.2,
\cite{Moore2014a}, for common gait computations and provide an example
processed trial to present the nature of the data. The tool was developed in
Python, is dependent on the SciPy Stack [NumPy~\citep{Walt2011},
SciPy~\citep{Jones2001}, matplotlib~\citep{Hunter2007},
Pandas~\citep{McKinney2010}, etc] and Octave~\citep{Octave2014}, and provides
two main classes: one to do basic gait data cleaning from D-Flow's output
files, \verb|DFlowData|, and a second to compute common gait variables of
interest, \verb|GaitData|.
